---
title: "Delayedflow Analysis in R tidyverse"
author: "Michael Stölzle"
date: "9/25/2020"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(delayedflow)
options(dplyr.summarise.inform=F)
```

This is a quick example how to use the delayedflow package in a R tidyverse environment.

```{r}
df <- read_tsv('https://raw.githubusercontent.com/modche/science_contr/master/4ezg.txt', col_types = cols())
```

```{r}
df %>% 
	group_by(filename) %>% 
	summarise(cdc = dfi_n(q = q, n = 1:180)$dfi, .groups = "keep", n = 0:180 ) %>% 
	ungroup() %>% 
	ggplot(aes(x=n, y = cdc)) +
		geom_line(aes(colour = filename)) +
		scale_x_continuous(breaks = c(0:6 * 30)) +
		theme_bw(14) +
		labs(title = "Delayed Flow Analysis for 4 catchments",
		     subtitle = "",
		     caption = "", 
			 colour = "CDCs",
		     x = "Block length N (days)", y = "DFI (-)")+
		theme(legend.position = c(0.80, 0.70))
	 
```


```{r, eval = TRUE}
df2 <- df %>% 
	group_by(filename) %>% 
	summarise(cdc = dfi_n(q = q, n = 1:180)$dfi, .groups = "keep", n = 0:180 ) %>% 
	ungroup()

df2


bp_df <- df2 %>% 
		group_by(filename) %>% 
		summarize(bps = find_bps(cdc, n_bp = 3, bp_max = 65)$bps_position) %>% 
		mutate(id = names(bps)) %>% 
		ungroup() %>% 
		pivot_wider(names_from = "id", values_from = "bps")

bp_df
```

```{r, echo = FALSE}
contr_df <- df2 %>% 
		group_by(filename) %>% 
		summarize(rel_contr = find_bps(cdc, n_bp = 3, bp_max = 65)$rel_contr) %>% 
		mutate(class = names(rel_contr)) %>% 
		ungroup()

contr_df
```

```{r, eval = FALSE, echo = FALSE}
contr_df_long <- contr_df %>% 
	pivot_longer(catchment1:catchment4, names_to = "name", values_to = "rel_contr")

	 # contr_df$type = factor(contr_df$type, 
	 # 					 levels = c("contr_4", "contr_3", "contr_2", "contr_1"),
	 # 					 labels = c("baseline", "intermediate_2", "intermediate_1", "short"))
```


```{r, eval = TRUE}
ggplot(data = contr_df) + 
	geom_col(aes(x = rel_contr, y = filename, fill = class), 
					width = 0.50, 
					colour = "black") +
	scale_fill_brewer(palette = "RdBu", 
					  direction = 1, 
					  guide = guide_legend(reverse = FALSE),
					  name = "Delay class") +
	scale_x_continuous(labels = scales::percent_format()) +
	theme_bw(14) +
	theme(legend.position = "bottom") +
	labs(title = "Delayed flow contributions",
     subtitle = "",
     caption = "", 
     x = "\nRelative contribution to streamflow", y = "")
```



## Explanation

In this example Catchment #1 has a high proportion of intermediate contributions (i.e. here snow melt from a high alpine catchment). Catchment #2 has > 50% baseline contributions that means it is highly groundwater-dominated. Comparing Catchment #4 vs. Catchment #3 the first one has more short-delayed contributions also visible in the rapid drop in the CDC curve above.
