---
title: "Workflow with delayflow package"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load package and data

```{r}
library(delayedflow)
q_obs <- q_data$q_obs
```

# Create CDCs from DFI

Now see how the DFI curve looks like:

```{r}
cdc <- dfi_n(q = q_obs, n = 1:120)

head(cdc)
tail(cdc)

plot(x = 0:120, y = cdc$dfi, 
	 type = "o", ylim = c(0,1),
	 ylab ="DFI", xlab = "Block length N (days)",
	 main = "Characteristic Delay Curve (CDC)")
```


# Finding breakpoints

```{r}
bps <- find_bps(dfi = cdc$dfi, 
			   n_bp = 3,
			   plotting = TRUE)
```

Looking at:

 - the breakpoint estimates, here 4, 20 and 65 days
 - output of the objective function
 - relative streamflow contributions between `filter_min`, the breakpoint(s) and `filter_max.`

```{r}
bps$bps_position
bps$bias
bps$rel_contr
```

# Estimation of nmax

```{r}
head(q_data)
find_nmax(q_data)
```

The results show that breakpoints at 65, 66 or 45 days (depending on low flow threshold) lead to a DFI value that equals the threshold.

```{r, warning=FALSE}
dfi_n(q = q_data$q_obs, n = c(44:46, 64:67), add_zero = FALSE)
```

